Automated segmentation and description of the internal morphology of human permanent teeth by means of micro-CT

### 2020-12-21 manuscript.tex
Version string like this? [ci skip]
This build is based on
https://github.com/habi/zmk-tooth-cohort-method-manuscript/commit/9bba6f14f1c6151dcef6a858c1d33aa070a70b5c.

This commit was created by the following CI build and job:
https://github.com/habi/zmk-tooth-cohort-method-manuscript/commit/9bba6f14f1c6151dcef6a858c1d33aa070a70b5c/checks
https://github.com/habi/zmk-tooth-cohort-method-manuscript/runs/436163268

A preprint of this manuscript is available on \emph{bioRxiv} at \url{https://doi.org/10.1101/2020.10.27.356998} and has been submitted to \href{https://bmcoralhealth.biomedcentral.com/}{\emph{BMC Oral Health}}.
This version of the manuscript \href{https://github.com/habi/zmk-tooth-cohort-method-manuscript/compare/f9b3333c625228f4f28211a34f381b9f87c430b0...a07ddbcdcccf1292f592df2bad976ebb3d53f15f}{has been updated} since the preprint deposition.

This manuscript
(\href{https://habi.github.io/zmk-tooth-cohort-method-manuscript/v/a07ddbcdcccf1292f592df2bad976ebb3d53f15f/}{permalink})
was automatically generated
from \href{https://github.com/habi/zmk-tooth-cohort-method-manuscript/tree/a07ddbcdcccf1292f592df2bad976ebb3d53f15f}{habi/zmk-tooth-cohort-method-manuscript@a07ddbc}
on December 21, 2020.

@@

We wrote a Jupyter (version 4.5.0) {[}\protect\hyperlink{ref-pQ6Wbz73}{21}{]} notebook with Python code (version 3.7.3) which allowed for scans to be checked as soon as they were reconstructed during scanning of the first items in the batch.
Re-runs of the notebook added newly scanned and reconstructed teeth to the analysis, facilitating preliminary checks and analysis of already scanned teeth.
The notebook used for the analysis presented in this manuscript is freely available online {[}\protect\hyperlink{ref-tZRGGuMm}{22}{]}.
The important steps of the analysis steps are described in detail below.

@@

We used \emph{Dask} (version 2.5.2) {[}\protect\hyperlink{ref-hj1CnyWB}{24}{]} to read the set of axial reconstruction PNG slices for each sample.
The reconstructions were stored on disk in the \emph{Zarr} storage format {[}\protect\hyperlink{ref-10Fk3ASPz}{25}{]}, an efficient, chunked and compressed array representation of the single images.
The zarr-representation of the reconstructions were used for further analysis and had a total size of 330 GB on disk.

>>>>

A preprint of this manuscript is available on \emph{bioRxiv} at \url{https://doi.org/10.1101/2020.10.27.356998} and has been submitted to \href{https://bmcoralhealth.biomedcentral.com/}{\emph{BMC Oral Health}}.
This version of the manuscript \href{https://github.com/habi/zmk-tooth-cohort-method-manuscript/compare/f9b3333c625228f4f28211a34f381b9f87c430b0...9bba6f14f1c6151dcef6a858c1d33aa070a70b5c}{has been updated} since the preprint deposition.

This manuscript
(\href{https://habi.github.io/zmk-tooth-cohort-method-manuscript/v/9bba6f14f1c6151dcef6a858c1d33aa070a70b5c/}{permalink})
was automatically generated
from \href{https://github.com/habi/zmk-tooth-cohort-method-manuscript/tree/9bba6f14f1c6151dcef6a858c1d33aa070a70b5c}{habi/zmk-tooth-cohort-method-manuscript@9bba6f1}
on December 21, 2020.

@@

We wrote a Jupyter {[}\protect\hyperlink{ref-pQ6Wbz73}{21}{]} notebook with Python code (version 3.7.3) which allowed for scans to be checked as soon as they were reconstructed during scanning of the first items in the batch.
Re-runs of the notebook added newly scanned and reconstructed teeth to the analysis, facilitating preliminary checks and analysis of already scanned teeth.
The notebook used for the analysis presented in this manuscript is freely available online {[}\protect\hyperlink{ref-tZRGGuMm}{22}{]}.
The important steps of the analysis steps are described in detail below.

@@

We used \emph{Dask} {[}\protect\hyperlink{ref-hj1CnyWB}{24}{]} to read the set of axial reconstruction PNG slices for each sample.
The reconstructions were stored on disk in the \emph{Zarr} storage format {[}\protect\hyperlink{ref-10Fk3ASPz}{25}{]}, an efficient, chunked and compressed array representation of the single images.
The zarr-representation of the reconstructions were used for further analysis and had a total size of 330 GB on disk.
